### 2019-11-28 chX_backmatter.tex
removed dyngen submodule
Added conferences, oral presentations, poster presentations and master student supervisions to backmatter.

\begin{itemize}
	\item \textbf{Cannoodt R}, Saelens W, Sichien D, Tavernier S, Janssens S, Guilliams M, Lambrecht B, De Preter K, Saeys Y. SCORPIUS improves trajectory inference and identifies novel modules in dendritic cell development. bioRxiv 079509. 2016 Oct.
	\item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. Computational methods for trajectory inference from single-cell transcriptomics. European journal of immunology. 2016 Nov;46(11):2496-506.
	\item \textbf{Cannoodt R}, Ruyssinck J, Ramon J, De Preter K, Saeys Y. IncGraph: Incremental graphlet counting for topology optimisation. PloS one. 2018 Apr 26;13(4):e0195997.
	\item Saelens W *, \textbf{Cannoodt R} *, Todorov H, Saeys Y. A comparison of single-cell trajectory inference methods. Nature biotechnology. 2019 May;37(5):547.
	%	\item \textbf{Cannoodt R}, Saelens W, Sichien D, Tavernier S, Janssens S, Guilliams M, Lambrecht B, De Preter K, Saeys Y. SCORPIUS: Fast, accurate, and robust single-cell pseudotime. In preparation.
	%	\item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. dyngen: Simulating developing single cells. In preparation.
	%	\item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. dyno: A toolkit for inferring, visualising, and interpreting trajectories. In preparation.
	%	\item \textbf{Cannoodt R}, Saeys Y, De Preter K. bred: Inferring single cell regulatory networks. In preparation. 
	%	\item \textbf{Cannoodt R}. Self-assessment in trajectory inference. In preparation.
\end{itemize}

@@

@@

We also helped maintain or extend other packages on Github, CRAN or Bioconductor on which our software depends. This includes speeding up parts of the dependency (slingshot), implementing new functionality (devtools, ParamHelpers, ranger, rlang), fixing bugs (proxyC, rlang, monocle, splatter, slingshot), becoming a maintainer of orphaned packages (diffusionMap, princurve, GillespieSSA), and extending the documentation (devtools, mlr, remotes). Several of these packages are mainstream R packages which receive millions of downloads per year (devtools, ranger, remotes, rlang).

@@

		\cranpkg{badger} & ctb & CRAN & 6240 & Query information and generate badge for using in README \\
		\biocpkgl{ClusterSignificance}{Clus\-ter\-Sig\-nif\-i\-cance} &  & Bioc & 935 & Assess if class clusters in dimensionality reduced data representations have a separation different from permuted data \\
		\cranpkg{devtools} & ctb & CRAN & 5'918'700 & Tools to make developing R packages easier \\
		\githubpkg{soedinglab}{merlot} & ctb & Github & \notavailable & Reconstructing lineage-tree topologies from scRNA-seq data \\
		\cranpkg{mlr} & ctb & CRAN & 176'330 & Machine Learning in R \\
		\biocpkg{monocle} & ctb & Bioc & 34'360 & Clustering, differential expression, and trajectory analysis for single-cell RNA-Seq \\
		\cranpkg{ParamHelpers} & ctb & CRAN & 150'775 & Helpers for Parameters in Black-Box Optimization, Tuning and Machine Learning \\
		\githubpkg{kieranrcampbell}{pseudogp} & ctb & Github & \notavailable & Probabilistic pseudotime for single-cell RNA-seq \\
		\cranpkg{ranger} & ctb & CRAN & 413'641 & A Fast Implementation of Random Forests \\
		\cranpkg{Rdimtools} & ctb & CRAN & 7367 & Dimension Reduction and Estimation Methods \\
		\cranpkg{remotes} & ctb & CRAN & 3'944'090 & R package installation from remote repositories \\
		\cranpkg{rlang} & ctb & CRAN & 13'269'115 & Functions for base types and core R and tidyverse features \\
		\githubpkg{aertslab}{SCope} & ctb & Github & \notavailable & Visualization of high dimensional single cell data \\
		\biocpkg{slingshot} & ctb & Bioc & 12'085 & Tools for ordering single-cell sequencing \\
		\biocpkg{splatter} & ctb & Bioc & 5015 & Simple simulation of single-cell RNA sequencing data \\
		\githubpkg{farrelja}{URD} & ctb & Github & \notavailable & Reconstructing branching trajectories from single-cell RNAseq data \\
		\githubpkg{ManuSetty}{wishbone} & ctb & Github & \notavailable & Identify bifurcating developmental trajectories from single-cell data \\\hline
	\end{tabularx}
\end{table}

%\subsection{Oral presentations}
%
%\subsection{Poster presentations}
%
%\subsection{Awards}
%
%\subsection{Courses / Workshops}
%
%\subsection{Conferences}
%
%\subsection{Student supervision}
%
%\subsection{Teaching}

@@

>>>>

\begin{itemize}
	\item \textbf{Cannoodt R}, Saelens W, Sichien D, Tavernier S, Janssens S, Guilliams M, Lambrecht B, De Preter K, Saeys Y. SCORPIUS improves trajectory inference and identifies novel modules in dendritic cell development. bioRxiv 079509. 2016 Oct.
	\item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. Computational methods for trajectory inference from single-cell transcriptomics. European journal of immunology. 2016 Nov;46(11):2496-506.
	\item \textbf{Cannoodt R}, Ruyssinck J, Ramon J, De Preter K, Saeys Y. IncGraph: Incremental graphlet counting for topology optimisation. PloS one. 2018 Apr 26;13(4):e0195997.
	\item Saelens W *, \textbf{Cannoodt R} *, Todorov H, Saeys Y. A comparison of single-cell trajectory inference methods. Nature biotechnology. 2019 May;37(5):547.
\end{itemize}

@@

\section{Conferences and meetings}

\begin{itemize}
  \item \textbf{Differential Network Medicine}, Antwerp, Belgium, 4-6 December 2013.
  \item \textbf{BeNeLux Bioinformatics Conference}, Brussels, Belgium, 9-10 December 2013.
  \item \textbf{OncoPoint}, Ghent, Belgium, 6 February 2014.
  \item \textbf{AISTATS}, Reykjavik, Iceland, 22-25 April 2014.
  \item \textbf{N2N Annual Symposium}, Ghent, Belgium, 21 May 2014.
  \item \textbf{Bioinformatics N2N Conference}, Ghent, Belgium, 21 May 2014.
  \item \textbf{BENELEARN}, Brussels, Belgium, 6 June 2014.
  \item \textbf{BeNeLux Bioinformatics Conference}, Luxembourg, 8-9 December 2014.
  \item \textbf{OncoPoint}, Ghent, Belgium, 11 February 2015.
  \item \textbf{Big Data to Bedside}, Ghent, Belgium, 1-2 April 2015.
  \item \textbf{BIG N2N symposium}, Ghent, Belgium, 21 May 2015.
  \item \textbf{BeNeLux Bioinformatics Conference}, Antwerp, Belgium, 7-8 December 2015
  \item \textbf{Single Cell Biology Workshop}, Ghent, Belgium, 15 January 2016.
  \item \textbf{Single Cell Biology}, Hinxton, United Kingdom, 8-10 March 2016.
  \item \textbf{BIG N2N symposium}, Ghent, Belgium, 19 May 2016.
  \item \textbf{CYTO}, Seattle, United States of America, 11-15 June 2016.
  \item \textbf{BENELEARN}, Kortrijk, Belgium, 12-13 September 2016.
  \item \textbf{Single Cell Genomics}, Hinxton, United Kingdom, 14-16 September 2016.
  \item \textbf{Single Cell Biology Workshop}, Ghent, Belgium, 15 January 2016.
  \item \textbf{VIB Seminar}, Veldhoven, Netherlands, 27-28 April 2017.
  \item \textbf{Keystone Symposia: Single Cell Omics}, Stockholm, Zweden, 26-30 May 2017. 
  \item \textbf{BeNeLux Bioinformatics Conference}, Louvain, België, 13-14 December 2017.
  \item \textbf{Single Cell Biology}, Hinxton, United Kingdom, 8-10 March 2018.
  \item \textbf{Keystone Symposia: Single Cell Biology}, Colorado, USA, 13-17 January 2019.
  \item \textbf{Human Cell Atlas}, Toronto, Canada, 29-31 July 2019.
\end{itemize}

\section{Courses / workshops}

\begin{itemize}
  \item \textbf{Differential Network Medicine}, Antwerp, Belgium, 4-6 September 2013.
  \item \textbf{Basics of Biology for Engineers}, Louvain, Belgium, 18-20 September 2013.
  \item \textbf{Metric Learning}, Louvain, Belgium, 15 October 2013.
  \item \textbf{Machine learning Summer School}, Reykjavik, Iceland, 25 April - 4 May 2014.
  \item \textbf{Effective Oral Presentations by Jean-Luc Doumont}, Ghent, Belgium, 3 February 2015.
  \item \textbf{RNA-Seq analysis for differential expression}, Ghent, Belgium, 24-27 April 2015.
  \item \textbf{BigData@UGent in practice}, Ghent, Belgium, 4 May 2015.
\end{itemize}

\section{Oral presentations}

\begin{itemize}
  \item Cannoodt R., Ruyssinck J., De Preter K., Dhaene T., Saeys Y. : Network inference by integrating biclustering and feature selection. \textbf{BeNeLux Bioinformatics Conference}, Brussels, Belgium, 9-10 December 2013.
  \item Cannoodt R., Ruyssinck J., De Preter K., Dhaene T., Saeys Y. : Network inference by integrating biclustering and feature selection. \textbf{IRC bioinformatics day}, Ghent, Belgium, 23 November 2013.
  \item Cannoodt R., De Preter K., Saeys Y. : Differential network inference for pediatric cancers. \textbf{Maestra meeting}, Ghent, Belgium, 14 March 2014.
  \item Cannoodt R., Beckers A., Van Cauwenbergh C., Speleman F., Saeys Y., De Preter K. : Differential module analysis in neuroblastoma regulatory networks. \textbf{Oncopoint}, Ghent, Belgium, 11 February 2015.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y.: Inferring developmental chronologies from single cell RNA, \textbf{BeNeLux Bioinformatics Conference}, Antwerp, Belgium, 7-8 December 2015.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y.: Inferring trajectories along dynamic processes from single-cell RNA-seq data. \textbf{Jean-Luc Doumont workshop}, Ghent, Belgium, 17 December 2015.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : SCORPIUS: Inferring trajectories along dynamic processes form single-cell RNA-seq data. \textbf{Single Cell Biology Workshop}, Ghent, Belgium, 15 January 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Improving marker gene discovery from high-dimensional single-cell snapshot data. \textbf{CYTO}, Seattle, United States of America, 11-15 June 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. \textbf{BENELEARN}, Kortrijk, Belgium, 12-13 September 2016.
  \item Cannoodt R., Saelens W., Sichien D., Tavernier S., Janssens S., Guilliams M., Lambrecht B., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with SCORPIUS identifies novel modules in dendritic cell development. \textbf{VIB Seminar}, Veldhoven, Nederland, 27-28 april 2017.
  \item Cannoodt R., Saelens W. : Automated building and unit testing, Docker and Singularity. \textbf{VIB Developers Meeting}, Ghent, Belgium, 25 January 2019.
  \item Cannoodt R., Saelens W., Todorov H., Saeys Y. : dynbenchmark, Assessing Accuracy, Robustness and Usability of Single-Cell Trajectory Inference methods. \textbf{Keystone Symposia: Single Cell Biology}, Colorado, USA, 13-17 January 2019.
\end{itemize}

\section{Poster presentations}

\begin{itemize}
  \item Cannoodt R., Ruyssinck J., De Preter K., Dhaene T., Saeys Y.: Network Inference by Integrating Biclustering and Feature Selection. \textbf{N2N Annual Symposium}, Ghent, Belgium, 21 May 2014.
  \item Cannoodt R., Van Cauwenbergh C., Beckers A., Speleman F., De Preter K., Saeys Y.: Differential Module Analysis in Neuroblastoma Regulatory Networks. \textbf{BeNeLux Bioinformatics Conference} 2014, Luxembourg, Belgium, 8-9 December 2014.
  \item Cannoodt R., Beckers A., Van Cauwenbergh C., Speleman F., De Preter K., Saeys Y.: Differential Module Analysis in Neuroblastoma Regulatory Networks, \textbf{BIG N2N symposium}, Ghent, Belgium, 21 May 2015.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. Single Cell Biology, Hinxton, United Kingdom, 8-10 March 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. \textbf{BIG N2N symposium}, \textbf{BIG N2N symposium}, Ghent, Belgium, 19 May 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Improving marker gene discovery from high-dimensional single-cell snapshot data. CYTO, Seattle, United States of America, 11-15 June 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. BENELEARN 2016, Kortrijk, Belgium, 12-13 September 2016.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y. : Unbiased modelling of dynamic processes with single-cell RNA-sequencing. Single Cell Genomics, Hinxton, United Kingdom, 14-16 September 2016.
  \item Cannoodt R., Saelens W., Sichien D., Tavernier S., Janssens S., Guilliams M., Lambrecht B., De Preter K., Saeys Y.: Unbiased modelling of dynamic processes with SCORPIUS identifies novel modules in dendritic cell development. \textbf{VIB Seminar}, Veldhoven, Netherlands, 27-28 April 2017.
  \item Cannoodt R., Saelens W., De Preter K., Saeys Y.: True single cell network inference: Modelling gene regulation of individual cells. \textbf{Keystone Symposia: Single Cell Omics}, Stockholm, Zweden, 26-30 May 2017. 
  \item Cannoodt R., Saelens W., Todorov H., Saeys Y.: Generalised framework for and comparison of 24 trajectory inference methods. \textbf{BeNeLux Bioinformatics Conference}, Louvain, België, 13-14 December 2017.
  \item Cannoodt R., Saelens W., Todorov H., Saeys Y. : A comparison of single-cell trajectory inference methods: towards more accurate and robust tools. \textbf{Single Cell Biology}, Hinxton, United Kingdom, 8-10 March 2018.
  \item Cannoodt R., Saelens W. : dynbenchmark, Assessing Accuracy, Robustness and Usability of Single-Cell Trajectory Inference methods. \textbf{Keystone Symposia: Single Cell Biology}, Colorado, USA, 13-17 January 2019.
\end{itemize}

\section{Master student supervision}

\begin{itemize}
  \item \textbf{Leen De Baets}. Identificatie van nieuwe kankergenen voor neuroblastoomonderzoek met machine learning. September 2013 -- June 2014.
  \item \textbf{Wouter Saelens}. Locale cel-type specifieke genexpressie in het myeloïde transcriptoom. September 2013 -- June 2014.
  \item \textbf{Charlotte De Vogelaere}. Quantitative evaluation of network inference methods for single-cell cancer regulomes. September 2015 -- June 2016.
  \item \textbf{Sofie Veys}. Comparative review of dimensionality reduction methods for high-throughput single-cell transcriptomics. September 2016 -- June 2017.
  \item \textbf{Chloë Guidi}. Het afleiden van dynamische grafen op basis van snapshot data. September 2016 -- June 2017.
  \item \textbf{Jarre Knockaert}. Inferentie van cellontwikkelingstrajecten met machine learning. September 2018 -- June 2019.
\end{itemize}

@@

We also helped maintain or extend other packages on Github, CRAN or Bioconductor on which our software depends. This includes speeding up parts of the dependency (slingshot), implementing new functionality (devtools, ParamHelpers, ranger, rlang), fixing bugs (proxyC, rlang, monocle, splatter, slingshot), becoming a maintainer of orphaned packages (diffusionMap, princurve, GillespieSSA), and extending the documentation (devtools, mlr, remotes, tidyverse). Several of these packages are mainstream R packages which receive millions of downloads per year (devtools, ranger, remotes, rlang, tidyverse).

@@

		\cranpkg{badger} & ctb & CRAN & 6240 & Query information and generate badge for using in README \\
		\biocpkgl{ClusterSignificance}{Clus\-ter\-Sig\-nif\-i\-cance} &  & Bioc & 935 & Assess if class clusters in dimensionality reduced data representations have a separation different from permuted data \\
		\cranpkg{devtools} & ctb & CRAN & 5'918'700 & Tools to make developing R packages easier \\
		\githubpkg{soedinglab}{merlot} & ctb & Github & \notavailable & Reconstructing lineage-tree topologies from scRNA-seq data \\
		\cranpkg{mlr} & ctb & CRAN & 176'330 & Machine Learning in R \\
		\biocpkg{monocle} & ctb & Bioc & 34'360 & Clustering, differential expression, and trajectory analysis for single-cell RNA-Seq \\
		\cranpkg{ParamHelpers} & ctb & CRAN & 150'775 & Helpers for Parameters in Black-Box Optimization, Tuning and Machine Learning \\
		\githubpkg{kieranrcampbell}{pseudogp} & ctb & Github & \notavailable & Probabilistic pseudotime for single-cell RNA-seq \\
		\cranpkg{ranger} & ctb & CRAN & 413'641 & A Fast Implementation of Random Forests \\
		\cranpkg{Rdimtools} & ctb & CRAN & 7367 & Dimension Reduction and Estimation Methods \\
		\cranpkg{remotes} & ctb & CRAN & 3'944'090 & R package installation from remote repositories \\
		\cranpkg{rlang} & ctb & CRAN & 13'269'115 & Functions for base types and core R and tidyverse features \\
		\githubpkg{aertslab}{SCope} & ctb & Github & \notavailable & Visualization of high dimensional single cell data \\
		\biocpkg{slingshot} & ctb & Bioc & 12'085 & Tools for ordering single-cell sequencing \\
		\biocpkg{splatter} & ctb & Bioc & 5015 & Simple simulation of single-cell RNA sequencing data \\
		\cranpkg{tidyverse} & ctb & CRAN &  & Easily install and load packages from the tidyverse \\
		\githubpkg{farrelja}{URD} & ctb & Github & \notavailable & Reconstructing branching trajectories from single-cell RNAseq data \\
		\githubpkg{ManuSetty}{wishbone} & ctb & Github & \notavailable & Identify bifurcating developmental trajectories from single-cell data \\\hline
	\end{tabularx}
\end{table}

@@

% TODO: copyright
